A Process for Emulating Comparative Oncology Trials with Real-world Evidence Studies (ENCORE): Process Development and Methodological Considerations for Oncology Real-World Data

### 2025-05-28 manuscript/manuscript.qmd
updated word count on title page after test run
typo

[**Manuscript word count:**]{.underline} 4,200 words / 8,000 words

@@

[**Supplementary material:**]{.underline} Supplementary figures and material

@@

A list of tentative, shortlisted primary candidates is presented in @tbl-rcts. The corresponding selection process is illustrated in the CONSORT diagrams (**Supplementary Figures 1-4**) and runner up candidate trials are listed in **Supplementary Table 1**. Naturally, the majority of shortliested trials cover advanced (locally advanced, inoperable, recurrent/progressive disease) or metastatic cancer populations because a large proportion of drug development efforts have recently focused on these settings. A key objective that we aim to explore with the selected trials is to achieve a better understanding how different disease settings (early, late), line settings (\[neo\]adjuvant, first line, advanced lines of therapy), therapy protocols (monotherapy, combination therapy) and clinical characteristics (all-comer versus complex genetic or immunological signatures) can be emulated using RWD. If more thorough feasibility assessments after applying all relevant eligibility criteria suggest that the threat of bias from mis-measurement of key study parameters or residual confounding remains high, or that the study size is not sufficient, then runner-up candidate trials will be considered instead.

>>>>

[**Manuscript word count:**]{.underline} 4,509 words / 8,000 words

@@

[**Supplementary material:**]{.underline} Supplementary figures, tables and material

@@

A list of tentative, shortlisted primary candidates is presented in @tbl-rcts. The corresponding selection process is illustrated in the CONSORT diagrams (**Supplementary Figures 1-4**) and runner up candidate trials are listed in **Supplementary Table 1**. Naturally, the majority of shortlisted trials cover advanced (locally advanced, inoperable, recurrent/progressive disease) or metastatic cancer populations because a large proportion of drug development efforts have recently focused on these settings. A key objective that we aim to explore with the selected trials is to achieve a better understanding how different disease settings (early, late), line settings (\[neo\]adjuvant, first line, advanced lines of therapy), therapy protocols (monotherapy, combination therapy) and clinical characteristics (all-comer versus complex genetic or immunological signatures) can be emulated using RWD. If more thorough feasibility assessments after applying all relevant eligibility criteria suggest that the threat of bias from mis-measurement of key study parameters or residual confounding remains high, or that the study size is not sufficient, then runner-up candidate trials will be considered instead.
